---
title: "Reading from the Web"
author: "Alison Elgass"
date: "10/10/2019"
output: github_document
---

```{r}
library(tidyverse)
library(rvest)
library(httr)
```

# Extracting Tibbles from HTML + CSS code

### Data from "National survey on drug use"
```{r}
drug_url = "http://samhda.s3-us-gov-west-1.amazonaws.com/s3fs-public/field-uploads/2k15StateFiles/NSDUHsaeShortTermCHG2015.htm"

drug_use_xml = read_html(drug_url) #read html code from above url

#extract the tables (15 total) from the webpage
drug_use_xml %>%
  html_nodes(css = "table")

#extract table 1 (marijuana use) of the 15 on the page
drug_use_xml %>%
  html_nodes(css = "table") %>% 
  .[[1]]

#now actually save table 1 data as a tibble
table_marj = drug_use_xml %>% 
  html_nodes(css = "table") %>% 
  .[[1]] %>%        #same as above
  html_table() %>%  
  slice(-1) %>%     #remove first row (captions)
  as_tibble()       #tibble
```
Success!!  

## Using CSS Selectors 
### Harry Potter IMDB example
```{r}
hpsaga_html = 
  read_html("https://www.imdb.com/list/ls000630791/")
```

Use selector gadget to find css tags
```{r}
title_vec =
  hpsaga_html %>% 
  html_nodes(".lister-item-header a") %>% 
  html_text()

gross_rev_vec = 
  hpsaga_html %>%
  html_nodes(".text-small:nth-child(7) span:nth-child(5)") %>%
  html_text()

runtime_vec = 
  hpsaga_html %>%
  html_nodes(".runtime") %>%
  html_text()
  
#now put them together
hpsaga_df = 
  tibble(
    title = title_vec,
    rev = gross_rev_vec,
    runtime = runtime_vec
  )
```

### Napoleon Dynamite Amazon Reviews example
```{r}
dynamite_url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1"

dynamite_html = read_html(dynamite_url)

#not working for right now...try again later
review_titles = 
  dynamite_html %>%
  html_nodes(".a-text-bold span") %>%
  html_text()

review_stars = 
  dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-rating") %>%
  html_text()

review_text = 
  dynamite_html %>%
  html_nodes(".review-text-content span") %>%
  html_text()

reviews = tibble(
  title = review_titles,
  stars = review_stars,
  text = review_text
)
```


# Using an API

### NYC water consumption
From website https://data.cityofnewyork.us/Environment/Water-Consumption-In-The-New-York-City/ia2d-e54m
1. Go to ... extra settings > API docs
2. Then toggle from json to csv and copy that link

```{r}
nyc_water = 
  GET("https://data.cityofnewyork.us/resource/waf7-5gvc.csv") %>% 
  content("parsed")
```
Success! Note this is super easy because API was straightforward and data is already in a nice table format.  

### Pokemon example

```{r}
poke = 
  GET("http://pokeapi.co/api/v2/pokemon/1") %>%
  content()

poke$name
poke$abilities
```


